Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-03-08 ch04-lrmhinf/paper.tex
Remove line thingie in figure
Short cpations for CH04

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/interpolation-show.tikz}
  \caption{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
  \TODO{top subplot has a line connecting the last to the first point...}
\label{fig:interpol-quantities}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/example-both.tikz}
  %\input{\thisDir/figs/example-LRM-SNR1.tikz}
  \caption{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \norm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gamma_{\mathrm{IG}}$) estimate are improved.
  The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
  Hence, $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
  \label{fig:exampleIntergrid}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/MC-runlength.tikz}
  %\input{figures/runLength.tikz}
  \caption{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
  However, the proposed $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$). A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:exampleIntergrid}. The shaded areas show the $\pm \sigma$ intervals which are mostly due to the noise.
  }
\label{fig:MC-run-length}
\end{figure}

@@

\begin{figure}
 \centering
 \input{\thisDir/figs/tpcrobust.tikz}
 \caption{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
 \label{fig:tpc}
\end{figure}

\begin{figure}
 \centering
 \input{\thisDir/figs/dualYoula.tikz}
 \caption{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
\label{fig:dualYoula}
\end{figure}

@@

\begin{figure}
 \centering
    \setlength{\figurewidth}{0.75\columnwidth}
    \setlength{\figureheight}{0.68\figurewidth}
    \input{\thisDir/figs/avis-frf.tikz}
 \caption{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsfirst{AVIS}.}
 \label{fig:avis-frf}
\end{figure}

@@

\begin{figure}
 \centering
    \setlength{\figurewidth}{0.75\columnwidth}
    \setlength{\figureheight}{0.68\figurewidth}
    % \input{\thisDir/figs/avis-delta-full.tikz}
    \TODOfig{split plots}
 \caption{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation. The data in the rectangle is also shown in \figref{fig:avisMeasZoom}.}
\label{fig:avisMeas}
\end{figure}

\begin{figure}
 \centering
    \setlength{\figurewidth}{0.75\columnwidth}
    \setlength{\figureheight}{0.68\figurewidth}
   \input{\thisDir/figs/avis4.tikz}
 \caption{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation. Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:avis4-LRM-hinf}, especially at $328\unit{Hz}$. The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid~\legref{leg:avis4-validation}, which reveals excellent interpolation properties and a similar peak value~\legref{leg:avis4-valid-hinf}.}
\label{fig:avisMeasZoom}
\end{figure}

>>>>

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/interpolation-show.tikz}
  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\set{1,\ldots,6}$.
  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
\label{fig:interpol-quantities}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/example-both.tikz}
  %\input{\thisDir/figs/example-LRM-SNR1.tikz}
  \caption[Example: FRF underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \norm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gamma_{\mathrm{IG}}$) estimate are improved.
  The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
  Hence, $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
  \label{fig:exampleIntergrid}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/MC-runlength.tikz}
  %\input{figures/runLength.tikz}
  \caption[Estimated $\gamma$ versus measurement time.]{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gamma_{\mathrm{FRF}}}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
  However, the proposed $\widehat{\norm[]{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$). A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:exampleIntergrid}. The shaded areas show the $\pm \sigma$ intervals which are mostly due to the noise.
  }
\label{fig:MC-run-length}
\end{figure}

@@

\begin{figure}
 \centering
 \input{\thisDir/figs/tpcrobust.tikz}
 \caption[Closed-loop block schematic.]{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
 \label{fig:tpc}
\end{figure}

\begin{figure}
 \centering
 \input{\thisDir/figs/dualYoula.tikz}
 \caption[Dual-Youla parametrization.]{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
\label{fig:dualYoula}
\end{figure}

@@

\begin{figure}
 \centering
    \setlength{\figurewidth}{0.75\columnwidth}
    \setlength{\figureheight}{0.68\figurewidth}
    \input{\thisDir/figs/avis-frf.tikz}
 \caption[\Glsentryname{FRF} and nominal model of \glsentryname{AVIS}.]{Measured \gls{FRF} \legref{m2t:plantFRF} and estimated parametric model $\hat{P}$ \legref{m2t:plantModel} of the \glsfirst{AVIS}.}
 \label{fig:avis-frf}
\end{figure}

@@

\begin{figure}
 \centering
    \setlength{\figurewidth}{0.75\columnwidth}
    \setlength{\figureheight}{0.68\figurewidth}
    % \input{\thisDir/figs/avis-delta-full.tikz}
    \TODOfig{split plots}
 \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling.]{Measured (dual-Youla) $\Delta$ for the \gls{AVIS} using the \gls{LRM} and the proposed interpolation. The data in the rectangle is also shown in \figref{fig:avisMeasZoom}.}
\label{fig:avisMeas}
\end{figure}

\begin{figure}
 \centering
    \setlength{\figurewidth}{0.75\columnwidth}
    \setlength{\figureheight}{0.68\figurewidth}
   \input{\thisDir/figs/avis4.tikz}
 \caption[$\Delta$ of the \glsentryname{AVIS}, estimated using local modeling (detail).]{Measured $\Delta$ for the \gls{AVIS} using the \gls{LRM}~\legref{leg:avis4-LRMi} and the proposed interpolation. Clearly, the \gls{LRM} leads to a higher peak value~\legref{leg:avis4-LRM-hinf}, especially at $328\unit{Hz}$. The validity of the LRM local parametric model is confirmed by the validation measurement at the dense frequency grid~\legref{leg:avis4-validation}, which reveals excellent interpolation properties and a similar peak value~\legref{leg:avis4-valid-hinf}.}
\label{fig:avisMeasZoom}
\end{figure}
